---
title: "Edits_to_data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Creating variables for clean data
```{r}
library(readxl)
library(jsonlite)
akcData <- read.csv("akc-data-latest.csv")
westminsterData <- read_excel("Westminster_data_clean.xlsx")
dogOriginData <- fromJSON("dog-breeds.json")
breedCoordinates <- read_excel("Breedcoordinates1.xlsx")
```

Removing Owner column
```{r}
westminsterData = subset(westminsterData, select = -c(Owner, Winner))
```

Removing unneeded Columns from AKC Data
```{r}
akcData = subset(akcData, select = -c(description, popularity, grooming_frequency_value, grooming_frequency_category, shedding_value, shedding_category, energy_level_value, trainability_value, trainability_category, demeanor_value, energy_level_category, demeanor_category))
```

Removing unneeded Row from AKC Data
```{r}
akcData <- akcData[-c(237, 17, 56, 245), ]
```

Changing values in westminster Dataset to match origin. gsub() didn't help because often order was flipped
```{r}
westminsterData[westminsterData=="Fox Terrier (Smooth)"] <- "Fox Terrier, Smooth"
westminsterData[westminsterData=="Fox Terrier (Wire)"] <- "Fox Terrier, Wire"
westminsterData[westminsterData=="Beagle (15 Inch)"] <- "Beagle"
westminsterData[westminsterData=="Spaniel (Cocker) Black[B]"] <- "English Cocker Spaniel"
westminsterData[westminsterData=="Spaniel (Cocker) ASCOB[B]"] <- "English Cocker Spaniel"
westminsterData[westminsterData=="Spaniel (Irish Water)"] <- "Irish Water Spaniel"
westminsterData[westminsterData=="Bichon Frise"] <- "Bichon Frisé"
westminsterData[westminsterData=="Bull Terrier (White)"] <- "Bull Terrier"
westminsterData[westminsterData=="Collie (Rough)"] <- "Collie, Rough"
westminsterData[westminsterData=="Poodle (Toy)"] <- "Poodle"
westminsterData[westminsterData=="Spaniel (Cocker) Parti"] <- "English Cocker Spaniel"
westminsterData[westminsterData=="Spaniel (Clumber)"] <- "English Cocker Spaniel"
westminsterData[westminsterData=="Poodle (Standard)"] <- "Poodle"
westminsterData[westminsterData=="Poodle (Miniature)"] <- "Poodle"
westminsterData[westminsterData=="Bull Terrier (Colored)"] <- "Bull Terrier"
westminsterData[westminsterData=="German Shepherd"] <- "German Shepherd Dog"
westminsterData[westminsterData=="Pointer (German Shorthaired)"] <- "Pointer"
westminsterData[westminsterData=="Setter (English)"] <- "English Setter"
westminsterData[westminsterData=="Spaniel (English Springer)"] <- "English Springer Spaniel"
```

Changing column name to join
```{r}
colnames(dogOriginData)[1] <- "Breed"
```

Joining dog Origin data with Westminster winners
```{r}
library(tidyverse)
tidywestminster <- left_join(westminsterData, dogOriginData, by = c("Breed"))
```

Deleting row for tidy data
```{r}
tidywestminster <- tidywestminster[-c(17), ]
```


Joining the Tidywestminter with coordinates
```{r}
tidywestminster = subset(tidywestminster, select = -c(origin))
tidywestminster[tidywestminster=="Germany, France"] <- "Germany"
tidywestminster[tidywestminster=="Germany, Poland"] <- "Poland"
tidywestminster[tidywestminster=="Spain, Belgium, France"] <- "France"
tidywestminster[tidywestminster=="Spain, Belgium"] <- "Spain"
finalDogData <- left_join(tidywestminster, breedCoordinates, by = c("Breed"))
finalDogData$origin[is.na(finalDogData$origin)] <- "Germany"
finalDogData$Coordinates[is.na(finalDogData$Coordinates)] <- "52.520008, 13.404954"
finalDogData$Latitude[is.na(finalDogData$Latitude)] <- 52.52001
finalDogData$Longitude[is.na(finalDogData$Longitude)] <- 13.404954
```

Turning links into html
```{r}
paste('<img src="' , finalDogData$imageURL, '" />')

```

Joining finalDogData with akc for height and weight characteristics
```{r}
akcData[akcData=="Smooth Fox Terrier"] <- "Fox Terrier, Smooth"
akcData[akcData=="Wire Fox Terrier"] <- "Fox Terrier, Wire"
akcData[akcData=="Beagle (15 Inch)"] <- "Beagle"
akcData[akcData=="Spaniel (Cocker) Black[B]"] <- "English Cocker Spaniel"
akcData[akcData=="Spaniel (Cocker) ASCOB[B]"] <- "English Cocker Spaniel"
akcData[akcData=="Spaniel (Irish Water)"] <- "Irish Water Spaniel"
akcData[akcData=="Bichon Frise"] <- "Bichon Frisé"
akcData[akcData=="Bull Terrier (White)"] <- "Bull Terrier"
akcData[akcData=="Collie"] <- "Collie, Rough"
akcData[akcData=="Poodle (Toy)"] <- "Poodle"
akcData[akcData=="Spaniel (Cocker) Parti"] <- "English Cocker Spaniel"
akcData[akcData=="Spaniel (Clumber)"] <- "English Cocker Spaniel"
akcData[akcData=="Poodle (Standard)"] <- "Poodle"
akcData[akcData=="Poodle (Miniature)"] <- "Poodle"
akcData[akcData=="Bull Terrier (Colored)"] <- "Bull Terrier"
akcData[akcData=="German Shepherd"] <- "German Shepherd Dog"
akcData[akcData=="Pointer (German Shorthaired)"] <- "Pointer"
akcData[akcData=="Setter (English)"] <- "English Setter"
akcData[akcData=="Spaniel (English Springer)"] <- "English Springer Spaniel"
colnames(akcData)[1] <- "Breed"
breedComp <- left_join(finalDogData, akcData, by = c("Breed"))
colnames(breedComp)[11] <- "Height"
colnames(breedComp)[13] <- "Weight"
colnames(breedComp)[15] <- "Life Expectancy"
colnames(breedComp)[16] <- "Group"
```

Making table with win frequency
```{r}
dogBreedUnique <- table(breedComp$Breed)
dogBreedUniqueDF <- data.frame(dogBreedUnique)
colnames(dogBreedUniqueDF)[1] <- "Breed"
dogBreedCompNarrow <- breedComp[c(2, 11, 13)]
dogBreedJoin <- left_join(dogBreedUniqueDF, dogBreedCompNarrow, by = c("Breed"))
colnames(dogBreedJoin)[2] <- "Frequency"
breedWinStats <- unique(dogBreedJoin)
```

Removing unneeded Row from breedWinStats
```{r}
breedWinStats <-breedWinStats[-c(28,30), ]
```

Rounding numbers to make them look pretty
```{r}
is.num <- sapply(breedComp, is.numeric)
breedComp[is.num] <- lapply(breedComp[is.num], round, 1)
```



